\documentclass[12pt]{article}
\usepackage[utf-8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{orange}{Zaika Frontend}}
\lhead{Interview Questions}
\cfoot{\thepage}

% Title Styling
\titleformat{\section}
{\normalfont\Large\bfseries\color{orange}}
{\thesection}{1em}{}

% Color definitions
\definecolor{darkblue}{RGB}{0, 51, 102}
\definecolor{orange}{RGB}{255, 140, 0}

\title{\textcolor{orange}{\textbf{Frontend Development Interview Questions}}}
\author{\textcolor{darkblue}{Zaika - Recipe Sharing Application}}
\date{\today}

\begin{document}

\maketitle

\begin{center}
\textcolor{darkblue}{\textit{A comprehensive set of questions about React, TypeScript, and Frontend Architecture}}
\end{center}

\vspace{1cm}

\section*{Core React Concepts}

\begin{enumerate}[label=\textbf{\arabic*.}, itemsep=0.5cm]

\item \textbf{What is React and why would you use it for building the Zaika application?}
\newline
\textcolor{gray}{\textit{Expected: Discuss component-based architecture, virtual DOM, reusability, and unidirectional data flow.}}

\item \textbf{Explain the difference between functional components and class components. Which one is used in Zaika?}
\newline
\textcolor{gray}{\textit{Expected: Functional components with hooks are used throughout Zaika. Explain why they're preferred.}}

\item \textbf{What is the useState hook and how is it used in the Landing page to manage form state?}
\newline
\textcolor{gray}{\textit{Expected: Discuss state initialization, setter function, and the [state, setState] pattern.}}

\item \textbf{Explain what the useContext hook does and how authentication context is implemented in Zaika.}
\newline
\textcolor{gray}{\textit{Expected: Context API for global state, avoiding prop drilling, AuthenticationContext implementation.}}

\item \textbf{What is the useLayoutEffect hook and why is it used to protect the Landing page route?}
\newline
\textcolor{gray}{\textit{Expected: Runs before rendering, synchronous, used for redirect logic, differs from useEffect.}}

\end{enumerate}

\section*{React Router and Navigation}

\begin{enumerate}[label=\textbf{\arabic*.}, itemsep=0.5cm, start=6]

\item \textbf{Explain React Router DOM v6 and how routing is configured in the App.tsx file.}
\newline
\textcolor{gray}{\textit{Expected: createBrowserRouter, RouterProvider, nested routes, path patterns like /dashboard/recipe/:id}}

\item \textbf{What are NavLink and useNavigate hooks? How are they used in the DashboardLayout?}
\newline
\textcolor{gray}{\textit{Expected: NavLink for navigation links with active styling, useNavigate for programmatic navigation.}}

\item \textbf{What is the Outlet component and what role does it play in the DashboardLayout?}
\newline
\textcolor{gray}{\textit{Expected: Placeholder for child routes, allows nested routing, renders child page content.}}

\item \textbf{How does the dynamic route parameter \texttt{:id} work in the recipe details page? Give an example.}
\newline
\textcolor{gray}{\textit{Expected: \texttt{/dashboard/recipe/:id} captures ID, useParams hook extracts it, used to fetch specific recipe.}}

\item \textbf{How would you implement route protection to ensure only authenticated users can access the dashboard?}
\newline
\textcolor{gray}{\textit{Expected: useLayoutEffect with token check, redirect to /, higher-order components, or route guards.}}

\end{enumerate}

\section*{State Management and Authentication}

\begin{enumerate}[label=\textbf{\arabic*.}, itemsep=0.5cm, start=11]

\item \textbf{Describe the complete authentication flow in Zaika from login to accessing the dashboard.}
\newline
\textcolor{gray}{\textit{Expected: User inputs → validation → API call → save token → context update → redirect.}}

\item \textbf{What is sessionStorage and how is it used to persist authentication tokens in Zaika?}
\newline
\textcolor{gray}{\textit{Expected: Browser API, temporary storage, cleared on tab close, used for JWT tokens.}}

\item \textbf{Explain what the AuthenticationContext provides and how it avoids prop drilling.}
\newline
\textcolor{gray}{\textit{Expected: Provides user, loading, onLogin, onLogout globally without passing through all components.}}

\item \textbf{How are axios interceptors configured and what do they do in the config/axios.ts file?}
\newline
\textcolor{gray}{\textit{Expected: Request interceptor adds token, response interceptor handles 401 errors and shows toasts.}}

\item \textbf{What happens when a user's session expires (401 error)? How is this handled?}
\newline
\textcolor{gray}{\textit{Expected: Interceptor catches 401, clears sessionStorage, shows warning toast, redirects to login.}}

\end{enumerate}

\section*{TypeScript and Type Safety}

\begin{enumerate}[label=\textbf{\arabic*.}, itemsep=0.5cm, start=16]

\item \textbf{What is TypeScript and why is it beneficial for the Zaika project?}
\newline
\textcolor{gray}{\textit{Expected: Type safety, catching errors at compile time, improved IDE support, better documentation.}}

\item \textbf{Examine the AUTH\_TYPE interface. Why is it important to define types for context values?}
\newline
\textcolor{gray}{\textit{Expected: Ensures components using context know what properties are available, prevents bugs.}}

\item \textbf{What is a generic type and how is useState typed as \texttt{useState<\_STATE>}?}
\newline
\textcolor{gray}{\textit{Expected: Generics add type parameter, useState<_STATE> tells TypeScript what shape state will have.}}

\item \textbf{Explain the difference between interface and type in TypeScript. Which is preferred in this project?}
\newline
\textcolor{gray}{\textit{Expected: Similar purposes, interfaces more extensible, types more flexible, both used in Zaika.}}

\item \textbf{How would you handle API responses that might have optional properties using TypeScript?}
\newline
\textcolor{gray}{\textit{Expected: Use optional properties with ?, Omit utility type, Partial<T>, discriminated unions.}}

\end{enumerate}

\section*{Styling and UI Components}

\begin{enumerate}[label=\textbf{\arabic*.}, itemsep=0.5cm, start=21]

\item \textbf{Explain Tailwind CSS and why it's used instead of traditional CSS. Give examples from the Landing page.}
\newline
\textcolor{gray}{\textit{Expected: Utility-first approach, \texttt{bg-black}, \texttt{text-white}, \texttt{md:w-1/2}, responsive design classes.}}

\end{enumerate}

\vspace{2cm}

\section*{Instructions for Candidates}

\begin{itemize}
    \item Each question tests different aspects of frontend development
    \item Some questions require code examples from the Zaika project
    \item Be prepared to discuss trade-offs and alternatives
    \item Show your understanding of React patterns, routing, and state management
    \item Demonstrate knowledge of TypeScript type system
    \item Explain how authentication and API integration works in real applications
\end{itemize}

\vspace{1cm}

\section*{Project Stack Summary}

\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Technology} & \textbf{Purpose} \\
\hline
React 18 & UI Library \\
TypeScript & Type Safety \\
React Router DOM v6 & Client-side Routing \\
Tailwind CSS & Styling \\
Axios & HTTP Requests \\
SWR & Data Fetching \& Caching \\
Vite & Build Tool \\
React Context API & Global State Management \\
\hline
\end{tabular}
\end{center}

\end{document}
